%-------------------------
% Resume in Latex
% Author : Javier Echeverria
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Javier Echeverria} \\ \vspace{1pt}
    \small 305-987-9702 $|$ \href{mailto:x@x.com}{\underline{javier.ruben.echeverria@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/javier-echeverria-780617195/}{\underline{linkedin.com/in/javier}} $|$
    \href{https://github.com/jrecheverria?tab=repositories}{\underline{github.com/jrecheverria}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of South Florida}{Tampa, FL}
      {Bachelor of Science in Computer Engineering}{July. 2016 -- December 2020}
      \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate Vice President - Software Engineer }{August 2022 -- Present}
      {Citi Bank}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Spearheaded the development of microservices using Spring Boot, enabling seamless access to JFrog Artifactory Services and enhancing the efficiency of the system.}
        \resumeItem{Implemented robust monitoring and metrics on services, significantly improving application resilience and ensuring a proactive approach to performance optimization.}
        \resumeItem{Demonstrated a commitment to operational excellence by providing on-call support during outages, contributing to swift issue resolution and minimizing downtime.}
        \resumeItem{Innovatively created custom Splunk dashboards to facilitate in-depth analysis of ongoing processes, providing actionable insights for continuous improvement and system optimization.}
      \resumeItemListEnd
      
    \resumeSubheading
      {SEP Software Engineer I / II}{February 2021 -- August 2022}
      {JP Morgan Chase}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Engineered a microservices-oriented ticketing system using Java Spring Boot to streamline operations for multiple product delivery teams.}
        \resumeItem{Accelerated the Cassandra record cleanup process by over 80\% for 1.7 million records through the implementation of a highly efficient, multi-threaded approach.}
        \resumeItem{Applied advanced Elasticsearch Java Client techniques to execute intricate nested aggregation queries, enhancing data retrieval and analysis capabilities.}
        \resumeItem{Deployed Kubernetes to proficiently manage the lifecycle of Docker containers, optimizing deployment and scalability for the overall system.}
    \resumeItemListEnd
    
  \resumeSubheading
      {Software Engineering Intern}{May 2019 -- July 2019}
      {Sofwerx}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Collaborated on a layered approach to reconnaissance of ultra-dense urban environments using object recognition, network fingerprinting, RF signatures, and machine learning.}
        \resumeItem{Utilized IBM Watson to develop, refine, and train real-time object detection and image classification models of security cameras with an average 95\% accuracy.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Brain-Computer Interface Research Assistant}{August 2018 -- December 2020}
      {University of South Florida}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Engineered an augmented reality application utilizing the Magic Leap AR headset, simulating emergency battlefield medical procedures. Developed the application using C\# and Unity game engine, showcasing proficiency in both programming and cutting-edge technology.}
         \resumeItem{Contributed 5K+ lines of code to an established codebase via Git}
        \resumeItemListEnd
      
    \resumeSubHeadingListEnd

 



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ABAHire.io} $|$ \emph{Typescript, React, Next.js, MySQL, Sanity, Clerk}}{June 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed ABA Hire, a full-stack web app, connecting 150+ users in the Applied Behavior Analysis field with job opportunities.}
            \resumeItem{Built an intuitive React front-end using Mantine UI, prioritizing best practices for a dynamic user experience.}
            \resumeItem{Designed a robust database structure to efficiently manage user information and relationships}
             \resumeItem{Utilized Next.js for seamless navigation and improved performance, deploying the platform on Vercel for scalability and fast load times.}
          \resumeItemListEnd
     \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, Typescript, Go, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Next.js, JUnit,  Springboot} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, Amazon Web Services, VS Code, IntelliJ} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
